

%%% Choose a language %%%

\newif\ifEN
% \ENtrue   % uncomment this for english
\ENfalse   % uncomment this for czech

%%% Configuration of the title page %%%

\def\ThesisTitleStyle{mff} % MFF style
%\def\ThesisTitleStyle{cuni} % uncomment for old-style with cuni.cz logo
%\def\ThesisTitleStyle{natur} % uncomment for nature faculty logo

\def\UKFaculty{Faculty of Mathematics and Physics}
%\def\UKFaculty{Faculty of Science}

\def\UKName{Charles University in Prague} % this is not used in the "mff" style

% Thesis type names, as used in several places in the title
\def\ThesisTypeTitle{\ifEN BACHELOR THESIS \else BAKALÁŘSKÁ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN MASTER THESIS \else DIPLOMOVÁ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN RIGOROUS THESIS \else RIGORÓZNÍ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN DOCTORAL THESIS \else DISERTAČNÍ PRÁCE \fi}
\def\ThesisGenitive{\ifEN bachelor \else bakalářské \fi}
%\def\ThesisGenitive{\ifEN master \else diplomové \fi}
%\def\ThesisGenitive{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisGenitive{\ifEN doctoral \else disertační \fi}
\def\ThesisAccusative{\ifEN bachelor \else bakalářskou \fi}
%\def\ThesisAccusative{\ifEN master \else diplomovou \fi}
%\def\ThesisAccusative{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisAccusative{\ifEN doctoral \else disertační \fi}



%%% Fill in your details %%%

% (Note: \xxx is a "ToDo label" which makes the unfilled visible. Remove it.)
\def\ThesisTitle{Možnosti návrhového vzoru Entity-Component-System: případová studie}
\def\ThesisAuthor{Petr Kotáb}
\def\YearSubmitted{2024}

% department assigned to the thesis
\def\Department{Katedra softwaru a výuky informatiky}
% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Katedra}

\def\Supervisor{Mgr. Pavel Ježek, Ph.D.}
\def\SupervisorsDepartment{Katedra distribuovaných a spolehlivých systémů}

% Study programme and specialization
\def\StudyProgramme{Informatika }
\def\StudyBranch{Počítačová grafika, vidění a vývoj her}

\def\Dedication{%
Dedication. \xxx{It is nice to say thanks to supervisors, friends, family, book authors and food providers.}
}

\def\AbstractEN{
The thesis focuses on measuring the performance of ECS libraries for the C\# programming language. However, instead of simple performance tests, this measurement is conducted on a game. The entire work consists of the game and the measurement. To use the game for measuring the performance of ECS libraries, it is necessary for it to be independent of any specific ECS library. To achieve this independence, the game uses an abstraction layer, which is used instead of a specific ECS library. Based on the problem, we defined which characteristics the game should meet, and then we designed and created it according to these characteristics. Before the actual measurement, we categorized the individual ECS libraries and formulated a hypothesis for them. Then we conducted several measurement, which confirmed this hypothesis.
}

% \xxx{Abstracts are an abstract form of art. Use the most precise, shortest sentences that state what problem the thesis addresses, how it is approached, pinpoint the exact result achieved, and describe the applications and significance of the results. Highlight anything novel that was discovered or improved by the thesis. Maximum length is 200 words, but try to fit into 120. Abstracts are often used for deciding if a reviewer will be suitable for the thesis; a well-written abstract thus increases the probability of getting a reviewer who will like the thesis.}
% ABSTRACT IS NOT A COPY OF YOUR THESIS ASSIGNMENT!

\def\AbstractCS{
Práce se zabývá měřením výkonu ECS knihoven pro programovací jazyk C\#. Ovšem namísto jednoduchých výkonostních testů toto měření provádíme na hře. Celá práce se skládá ze hry a měření. Aby bylo možné hru používat pro měření výkonu ECS knihoven, je nutné, aby byla nezávislá na konkrétní ECS knihovně. Pro dosažení této nezávislosti hra používá abstrakční vrstvu, se kterou pracuje namísto konkrétní ECS knihovny. Na základě problému jsme si definovali charakteristiky, které by hra měla splňovat, a poté jsme ji na základě těchto charakteristik navrhli a vytvořili. Před samotným měřením jsme jednotlivé ECS knihovny rozdělili do kategorií a pro tyto kategorie stanovili hypotézu. Poté jsme provedli několik měření, která tuto hypotézu potvrdila.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces.
% Keywords are useful for indexing and searching for the theses by topic.
\def\Keywords{
    {návrhový vzor}
    {Entity-Component-System}
    {počítačové hry}
    {simulace}
    {případová studie}
}

% If your abstracts are long and do not fit in the infopage, you can make the
% fonts a bit smaller by this setting. (Also, you should try to compress your abstract more.)
% Alternatively, consider increasing the size of the page by uncommenting the
% geometry modification in thesis.tex.
%\def\InfoPageFont{}
\def\InfoPageFont{\small}  %uncomment to decrease font size

\ifEN\relax\else
% If you are writing a czech thesis, you additionally need to fill in the
% english translation of the metadata here!
\def\ThesisTitleEN{Exploring Options of Entity-Component-System Design Pattern: A Case Study}
\def\DepartmentEN{Department of software and computer science education}
\def\DeptTypeEN{Department}
\def\SupervisorsDepartmentEN{Department of Distributed and Dependable Systems}
\def\StudyProgrammeEN{Computer Science}
\def\StudyBranchEN{Computer Graphics, Vision and Game Development}
\def\KeywordsEN{
    {design pattern}
    {Entity-Component-System}
    {computer games}
    {simulation}
    {case study}
}
\fi
